The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-09-13 analysis/paper/paper.qmd
Update topic model variable names

# What are the most probable topics in the entire collection?
topicProportions <- colSums(theta) / nDocs(emu_dtm)  # mean probabilities over all paragraphs
names(topicProportions) <- topic_names     # assign the topic names we created before
sort(topicProportions, decreasing = TRUE) # show summed proportions in decreased order

@@

# How many documents are with the highest probability in each topic?
K = 5
countsOfPrimaryTopics <- rep(0, K)
names(countsOfPrimaryTopics) <- topic_names
for (i in 1:nDocs(emu_dtm)) {
  topicsPerDoc <- theta[i, ] # select topic distribution for document i
  # get first element position from ordered list
  primaryTopic <- order(topicsPerDoc, decreasing = TRUE)[1] 
  countsOfPrimaryTopics[primaryTopic] <- countsOfPrimaryTopics[primaryTopic] + 1
}
sort(countsOfPrimaryTopics, decreasing = TRUE)

@@

topicToFilter <- 6  # you can set this manually ...
# ... or have it selected by a term in the topic name (e.g. 'children')
topicToFilter <- grep('river', topic_names)[1] 
topicThreshold <- 0.2
selectedDocumentIndexes <- which(theta[, topicToFilter] >= topicThreshold)
filteredCorpus <- emu_theses[selectedDocumentIndexes,]
# show length of filtered corpus
filteredCorpus
```

@@

N = 82
topic_prop_per_year <- theta[1:N,]
colnames(topic_prop_per_year) <- topic_names

# TODO change to pivot_longer
vizDataFrameWithYear <- melt(cbind(data.frame(topic_prop_per_year), 
                           document = factor(rownames(topic_prop_per_year))), 
                     variable.name = "topic", id.vars = "document") |> 
    left_join(select(emu_theses, ID, "year" = graduation_year), by = c("document" = "ID"))

@@

# Convert DTM into JSON required by the LDAvis package
json <- LDAvis::createJSON(
  phi = beta, 
  theta = theta, 
  doc.length = rowSums(as.matrix(emu_dtm)), 
  vocab = colnames(emu_dtm), 
  term.frequency = colSums(as.matrix(emu_dtm)),
  mds.method = svd_tsne,
  plot.opts = list(xlab="", ylab="")
)

>>>>

# What are the most probable topics in the entire collection?
topicProportions <- colSums(theta_5) / nDocs(emu_dtm)  # mean probabilities over all paragraphs
names(topicProportions) <- topic_names_5     # assign the topic names we created before
sort(topicProportions, decreasing = TRUE) # show summed proportions in decreased order

@@

# How many documents are with the highest probability in each topic?
K = 5
countsOfPrimaryTopics <- rep(0, K)
names(countsOfPrimaryTopics) <- topic_names_5
for (i in 1:nDocs(emu_dtm)) {
  topicsPerDoc <- theta_5[i, ] # select topic distribution for document i
  # get first element position from ordered list
  primaryTopic <- order(topicsPerDoc, decreasing = TRUE)[1] 
  countsOfPrimaryTopics[primaryTopic] <- countsOfPrimaryTopics[primaryTopic] + 1
}
sort(countsOfPrimaryTopics, decreasing = TRUE)

@@

topicToFilter <- 6  # you can set this manually ...
# ... or have it selected by a term in the topic name (e.g. 'children')
topicToFilter <- grep('river', topic_names_5)[1] 
topicThreshold <- 0.2
selectedDocumentIndexes <- which(theta_5[, topicToFilter] >= topicThreshold)
filteredCorpus <- emu[selectedDocumentIndexes,]
# show length of filtered corpus
filteredCorpus
```

@@

N = 82
topic_prop_per_year <- theta_5[1:N,]
colnames(topic_prop_per_year) <- topic_names_5

# TODO change to pivot_longer
vizDataFrameWithYear <- melt(cbind(data.frame(topic_prop_per_year), 
                           document = factor(rownames(topic_prop_per_year))), 
                     variable.name = "topic", id.vars = "document") |> 
    left_join(select(emu, ID, "year" = graduation_year), by = c("document" = "ID"))

@@

# Convert DTM into JSON required by the LDAvis package
json <- LDAvis::createJSON(
  phi = beta_5, 
  theta = theta_5, 
  doc.length = rowSums(as.matrix(emu_dtm)), 
  vocab = colnames(emu_dtm), 
  term.frequency = colSums(as.matrix(emu_dtm)),
  mds.method = svd_tsne,
  plot.opts = list(xlab="", ylab="")
)
